%-------------------------
% Resume in Latex
% Author : Gurleen Wadhwa
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Gurleen Wadhwa} \\ \vspace{1pt}
    \small (902)-412-5241 $|$ \href{mailto:gurleen.wadhwa@dal.ca}{\underline{gurleen.wadhwa@dal.ca}} $|$ 
    \href{https://www.linkedin.com/in/gurleen-wadhwa-56829a1a0/}{\underline{LinkedIn}} $|$
    \href{https://github.com/gurleenwadhwa-13}{\underline{GitHub}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dalhousie University}{Jan 2020 -- April 2024} 
      {Bachelor of Computer Science}{Halifax, NS}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
% -----------Multiple Positions Heading Structure-----------
%    \resumeSubSubheading
%     {Software Engineer }{DATES COME HERE}
%     \resumeItemListStart
%        \resumeItem{BULLET POINTS FOR EXPERIENCES}
%          {EXAMPLE:Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Student Navigator (IT Help Desk)}{Jan 2023 -- Present}
      {Dalhousie University}{Halifax, NS}
      \resumeItemListStart
        \resumeItem{Providing technical assistance to faculty, staff, students, and alumni.}
        \resumeItem{Assisted Faculty, Students, and Alumni with downloading open-source software and getting licenses, setting up Virtual Private Networks(VPN), as well as troubleshooting any related issues.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Quality Engineer Intern}{Jan 2022 -- May 2022}
      {Introhive}{Remote(Canada)}
      \resumeItemListStart
        \resumeItem{Performed manual testing on pull requests to prevent the introduction of new bugs to end-users.}
        \resumeItem{Conducted routine testing in both local and staging environments, achieving an accuracy rate of over 85\%.}
        \resumeItem{Re-crafted test cases for older products, resulting in a 65\% increase in test coverage and greater ease of comprehension.}
        \resumeItem{Participated in daily standup meetings within an Agile development framework.}
        \resumeItem{Acquired knowledge of Agile software development life cycle (SDLC) methodologies and operational continuous integration/continuous delivery (CI/CD) pipelines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\textbf{Quick Cash} $|$ \emph{Java, Android SDK, Firebase Realtime Database, Git, GitLab}}{Sept 2022 -- Dec 2022}
          \resumeItemListStart
            \resumeItem{Developed an Android application that functions as a job-board platform, designed to assist students in finding part-time and casual employment opportunities within their vicinity.}
            \resumeItem{Constructed the application from the ground up, incorporating geolocation features via the Google Maps API, a payment interface utilizing the PayPal API, and a recommendation engine to help employers identify suitable candidates based on their previous job experience.}
            \resumeItem{Personally contributed to the project by integrating filter and search functionalities.}
            \resumeItem{Worked in a team of 6 developers and followed Agile Principles.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Music Player} $|$ \emph{JavaScript, ReactJS, Redux Toolkit, Tailwind CSS, Git, GitHub}}{Feb 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Resulted in an end product consisting of a front-end component of a music streaming service, which accessed data through APIs.}
            \resumeItem{Employed the Shazam API in order to retrieve artist and song data by means of the RapidAPI library and used Redux for state management.}
            \resumeItem{Implemented React Best practices for file-structure and directory management.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Game of Tetris} $|$ \emph{JavaScript, HTML, CSS, FlexBox, Git, GitHub}}{Jan 2023 -- Feb 2023}
          \resumeItemListStart
            \resumeItem{Created the iconic game of Tetris as a starting point of learning the language, used basic data structures like 2D Arrays and HashMaps.}
            \resumeItem{Practiced Advanced CSS Flexbox and Z-index concepts.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, C/C++, SQL, HTML/CSS, JavaScript} \\
     \textbf{Frameworks}{: Spring Boot, JUnit, React} \\
     \textbf{Developer Tools}{: Git, GCC Compiler Tools, VS Code, PyCharm, IntelliJ, Android Studio, VIM, GitHub, GitLab} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
